What is the Effect of X on Y?

### 2023-10-26 latex-slides/slides.tex
Update table to better highlight features

  \medskip
  \begin{table}[h]
    \centering
    \begin{tabular}{lc}
      \toprule
      & (1) \\
      \midrule
      \rowcolor<2>{alice!15!white}Treatment dummy & \cellcolor<1>{accent!15!white} 0.0694* \\
      \rowcolor<2>{alice!15!white}& (0.0401) \\
      \rowcolor<3>{alice!15!white} Constant & -1.2238*** \\
      \rowcolor<3>{alice!15!white} & (0.0764)  \\
      \hline
      Observations & 1,673  \\
      R-squared & 0.0401 \\

      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

@@

        \only<1>{
          \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
          &  (0.149) & (0.129) \markbottomright{ex1} \\
        }
        \only<2>{
          Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
          &  (0.149) & (0.129) \\
        }
        No Special Privileges & -0.104 & $-$0.103  \\ 
        & (0.135) & (0.129) \\
        Opportunity to Learn & 0.249 & 0.238$^{*}$ \\ 
        & (0.160) & (0.139) \\

>>>>

  \bigskip
  \begin{table}[h]
    \centering
    \begin{tabular}{l cc}
      \toprule
      & (1) & (2) \\
      \midrule
      Treatment dummy & \cellcolor<1>{accent!15!white} 0.0694* & \cellcolor<2>{accent!15!white} 0.0713** \\
      & (0.0401) & (0.0381) \\
      \hline
      \rowcolor<3>{accent!15!white} State Fixed Effects & & $\checkmark$ \\
      Observations & 1,673 & 1,673 \\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

@@

        \only<2>{
          \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
          &  (0.149) & (0.129) \markbottomright{ex1} \\
        }
        \only<1>{
          Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
          &  (0.149) & (0.129) \\
        }
        No Special Privileges & -0.104 & $-$0.103  \\ 
        & (0.135) & (0.129) \\
        Opportunity to Learn & 0.249 & 0.238$^{*}$ \\ 
        & (0.160) & (0.139) \\
